%!TEX TS-program = lualatex
%% vim: set fenc=utf-8 ts=1 sw=0 sts=0 sr et si tw=0 fdm=marker fmr=<<<,>>>:
%%
%% Scientific paper for `Phone Controlled Car`
%%

% <<< Basic document settings
\documentclass[
 fontsize  = 11,                 % font size
 %papersize = a4,                 % paper size
 %language  = {english,romanian}, % document language(s) (last language in a list is the main language)
%
 %imagesupport = true, % load packages, custom macros and customizations for images
 %mathsupport  = true, % load packages, custom macros and customizations for math
 tablesupport = true, % load packages, custom macros and customizations for tables
 urlsupport   = true, % load packages, custom macros and customizations for URLs
%
 %docstyle                   = article,       % general document style [ article | book ]
 %docstyleChapterClearpage   = false,         % whether to put chapter on a new page
 %docstyleChapterStyle       = article,       % chapter heading style (see memman.pdf sec. 6.5.1)
 %docstylePageLayout         = oneside,       % page layout [ oneside | twoside ]
 %docstyleSectioningOpen     = any,           % on which side should document divisions open [ any | left | right ]
 docstyleTitleStyle         = scientificpaper % style of \maketitle [ default | eseuribacromana ]
 %docstyleToCClearpageBefore = false,         % whether to put ToC on a new page
 %docstyleToCClearpageAfter  = false,         % whether to put content after the ToC on a new page
%
 %draft, % draft mode
]{my_style}
% >>>

% <<< Packages
% >>>

% <<< Other settings
% <<< Image location
%\graphicspath{ {./img/} }
% >>>
% >>>

% <<< Basic document info
\title{Phone Controlled Car}
\author{Dobrete Andrei-Robert, Mihalache Denisa Ana-Maria}
\moreinfo
{
 University: Polytechnic University of Bucharest;
 Faculty: Industrial Engineering and Robotics;
 Specialization: Robotics;
 Year of study: 1;
 e-mail: \inserturl{mailto://andy3153@protonmail.com}, \inserturl{mailto://mihalachedenisa8@gmail.com}
 \\\vspace{2mm}
 Scientific leader: prof. Ivan Andrei Mario
}
\projecturl{https://github.com/Andy3153/phone-controlled-car}
% >>>

\begin{document}
 \maketitle       % generate title

 % <<< Abstract
 \begin{abstract}
  \textbf{Summary:}
  This project implements a Bluetooth-enabled vehicle controlled via smartphone, providing a flexible foundation that can be adapted for numerous use cases.

  \textbf{Key words:}
  car, robot, bluetooth, remote control.
 \end{abstract}
 % >>>

 \tableofcontents % generate ToC

 % <<< Document content
 % <<< Introduction
 \chapter{Introduction}
 The rapid development of low-cost microcontroller platforms has created new possibilities for the development of versatile robotic systems.
 The Arduino ecosystem has emerged as the most popular open-source prototyping platform because of its accessible hardware architecture, extensive library support and the large community around it.
 By integrating Bluetooth communication, it becomes possible to create a wireless link between a microcontroller-based vehicle and a smartphone, enabling real-time control via a dedicated mobile application.

 This paper presents the design, implementation and source code of a smartphone controlled robotic car built upon the Arduino platform.
 The system uses the \texttt{Serial Port Profile (SPP)} of the Bluetooth standard to transmit directional control signals from a mobile device to the Bluetooth module (\texttt{HC-05}), which gets parsed by the microcontroller to drive a motor driver module (\texttt{L298N}) that actuates the vehicle's DC motors.
 The modularity, simplicity and extensibility of the architecture allow it to serve as a foundational platform for a wide range of applications.
 These include, but are not limited to:
 \begin{itemize}
  \item remote-controlled (RC) navigation,
  \item autonomous maze-solving through wall-following algorithms,
  \item obstacle avoidance via ultrasonic or infrared proximity sensors,
  \item line-following using reflectance sensor arrays,
  \item robotic manipulation through the integration of a robotic arm.
 \end{itemize}

 The flexibility of the platform makes it well-suited for both educational environments and practical deployment scenarios.
 % >>>

 % <<< Materials and Methods
 \chapter{Materials and Methods}
 % <<< Hardware Components
 \section{Hardware Components}
 The main required hardware components are listed as follows:

 \inserttbl{|p{35mm}|l|p{94mm}|}<Hardware components>
 {
  \hline
  \textbf{component}                    & \textbf{model}       & \textbf{link} \\\hline
  \hline
  battery cells                         & \texttt{18650}       & \inserturl{https://www.optimusdigital.ro/ro/acumulatori-li-ion/3152-acumulator-samsung-li-ion-3000-mah-18650-inr18650-30q.html}\\\hline
  bluetooth module                      & \texttt{HC-05}       & \inserturl{https://www.optimusdigital.ro/ro/wireless-bluetooth/153-modul-bluetooth-master-slave-hc-05-cu-adaptor.html}\\\hline
  development board                     & \texttt{Arduino Uno} & \inserturl{https://www.optimusdigital.ro/ro/placi-avr/4561-placa-de-dezvoltare-compatibila-cu-arduino-uno-r3-atmega328p-atmega16u2-cablu-50-cm.html}\\\hline
  motor driver module                   & \texttt{L298N}       & \inserturl{https://www.optimusdigital.ro/ro/drivere-de-motoare-cu-perii/145-driver-de-motoare-dual-l298n.html}\\\hline
  motor with reduction gears and wheels & -                    & \inserturl{https://www.optimusdigital.ro/ro/motoare-altele/139-motor-cu-reductor-si-roata.html}\\\hline
 }
 % >>>
 % >>>
 % >>>
\end{document}
